\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{// All comments are NOT created equal}

### 2014-12-06 Proposal.tex
submitted version

Visual and normal tree-like graph language have different primitives and it is interesting how one can be mapped to the other. When we consider tree-like graphs, there are two structural primitives, namely the nodes, which represent concepts, and the edges, which represent relations between nodes. Additionally we can add semantic primitives like attributes to the concepts and to the relations to show what kind of a relation it is. In normal graphs a relation between two nodes is often quite simple: there is one node that acts as the subject, one node that acts as an object, and the relation that acts like a predicate. Thus we can, for instance, express that the Pythagorean Theorem depends on information about right angles (similar to figure \ref{fig:Annie-context}). These structural primitives and semantic primitives provide the basics that graphs can be built on.\\

@@

The exact layout of the frames and the best visualization of the relation between the frames is to be determined but figure \ref{fig:Annie-relsize} can be seen as a first draft. Ideally the added expressiveness that Impress.js offers should lead to Annie having the information about the Pythagorean theorem on a slide-like structure while having all the information the Pythagorean theorem depends on easily accessible so that she can reach \textit{course-old} information easily. \\

>>>>

Visual and normal tree-like graph language have different primitives and it is interesting how the primitives of the former can be mapped to the primitives of the latter. When we consider tree-like graphs, there are two structural primitives, namely the nodes, which represent concepts, and the edges, which represent relations between nodes. Additionally we can add semantic primitives like attributes to the concepts and to the relations to add information or to show what kind of a relation it is. In normal graphs a relation between two nodes is often quite simple: there is one node that acts as the subject, one node that acts as an object, and the relation that acts as a predicate. Thus we can, for instance, express that the Pythagorean theorem depends on information about right angles (similar to figure \ref{fig:Annie-context}). These structural primitives and semantic primitives provide the basics that graphs can be built on.\\

@@

The exact layout of the frames and the best visualization of the relations between the frames is to be determined but figure \ref{fig:Annie-relsize} can be seen as a first draft. Ideally the added expressiveness that Impress.js offers should lead to Annie having the information about the Pythagorean theorem on a slide-like structure, while having all the information the Pythagorean theorem depends on easily accessible so that she can reach \textit{course-old} information easily. \\
